---
title: "CheckBlenAsymmetry"
author: "Xiang Ji"
date: "February 4, 2016"
output: html_document
---

Load data from All.RData

```{r}
rm(list=ls())  # clean up workspace
load("/Users/Xiang/GitFolders/IGCCodonSimulation/All.RData")

paml.path <- "/Users/Xiang/GitFolders/IGCCodonSimulation/"
IGC.geo.list <- c(3.0, 10.0, 50.0, 100.0, 500.0)

# check.paml.path <- "/Users/xji3/TempChecking/IGCCodonSimulation/"
# #IGC.geo.list <- c(3.0)
# for (IGC.geo in IGC.geo.list){
#   for (localtree in 1:3){
#     summary_mat <- NULL
#     IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
#     file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "estimatedTau", "paml", "unrooted", "LocalTree", toString(localtree), "summary.txt", sep = "_")
#     for (sim.num in 0:(num.sim - 1)){
#       summary_file <- paste(check.paml.path, file.name, sep = "")
#       if (file.exists(summary_file)){
#         all <- readLines(summary_file, n = -1)
#         col.names <- strsplit(all[1], ' ')[[1]][-1]
#         row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
#         summary_mat <- as.matrix(read.table(summary_file, 
#                                             row.names = row.names, 
#                                             col.names = col.names))
#         
#       }
#     }
#     assign(paste("check_PAML", "estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "LocalTree", toString(localtree), "summary", sep = "_"), summary_mat)}
# }



for (IGC.geo in IGC.geo.list){
  for (localtree in 1:3){
    summary_mat <- NULL
    IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
    file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "estimatedTau", "paml", "unrooted", "LocalTree", toString(localtree), "summary.txt", sep = "_")
    for (sim.num in 0:(num.sim - 1)){
      summary_file <- paste(paml.path, file.name, sep = "")
      if (file.exists(summary_file)){
        all <- readLines(summary_file, n = -1)
        col.names <- strsplit(all[1], ' ')[[1]][-1]
        row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
        summary_mat <- as.matrix(read.table(summary_file, 
                                            row.names = row.names, 
                                            col.names = col.names))
        
      }
    }
    assign(paste("PAML", "estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "LocalTree", toString(localtree), "summary", sep = "_"), summary_mat)}
}


# Read in new PAML results
data.path <- paste(paralog, "",sep = "/")
for (IGC.geo in IGC.geo.list){
  summary_mat <- NULL
  IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
  file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "estimatedTau", "paml", "unrooted", "1stTree", "summary.txt", sep = "_")
  for (sim.num in 0:(num.sim - 1)){
    summary_file <- paste(paml.path, file.name, sep = "")
    if (file.exists(summary_file)){
      all <- readLines(summary_file, n = -1)
      col.names <- strsplit(all[1], ' ')[[1]][-1]
      row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
      summary_mat <- as.matrix(read.table(summary_file, 
                                          row.names = row.names, 
                                          col.names = col.names))
      
    }
  }
  assign(paste("PAML", "estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "1stTree", "summary", sep = "_"), summary_mat)
}

for (IGC.geo in IGC.geo.list){
  summary_mat <- NULL
  IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
  file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "estimatedTau", "paml", "unrooted", "2ndTree", "summary.txt", sep = "_")
  for (sim.num in 0:(num.sim - 1)){
    summary_file <- paste(paml.path, file.name, sep = "")
    if (file.exists(summary_file)){
      all <- readLines(summary_file, n = -1)
      col.names <- strsplit(all[1], ' ')[[1]][-1]
      row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
      summary_mat <- as.matrix(read.table(summary_file, 
                                          row.names = row.names, 
                                          col.names = col.names))
      
    }
  }
  assign(paste("PAML", "estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "2ndTree", "summary", sep = "_"), summary_mat)
}

# for (IGC.geo in IGC.geo.list){
#   summary_mat <- NULL
#   IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
#   file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "10Tau", "paml", "unrooted", "1stTree", "summary.txt", sep = "_")
#   for (sim.num in 0:(num.sim - 1)){
#     summary_file <- paste(paml.path, file.name, sep = "")
#     if (file.exists(summary_file)){
#       all <- readLines(summary_file, n = -1)
#       col.names <- strsplit(all[1], ' ')[[1]][-1]
#       row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
#       summary_mat <- as.matrix(read.table(summary_file, 
#                                           row.names = row.names, 
#                                           col.names = col.names))
#       
#     }
#   }
#   assign(paste("PAML", "10Tau", paste(toString(IGC.geo), ".0", sep = ""), "1stTree", "summary", sep = "_"), summary_mat)
# }
# 
# for (IGC.geo in IGC.geo.list){
#   summary_mat <- NULL
#   IGC.geo.path <- paste("IGCgeo_", toString(IGC.geo), ".0/", sep = "")
#   file.name <- paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "10Tau", "paml", "unrooted", "2ndTree", "summary.txt", sep = "_")
#   for (sim.num in 0:(num.sim - 1)){
#     summary_file <- paste(paml.path, file.name, sep = "")
#     if (file.exists(summary_file)){
#       all <- readLines(summary_file, n = -1)
#       col.names <- strsplit(all[1], ' ')[[1]][-1]
#       row.names <- strsplit(all[length(all)], ' ')[[1]][-1]
#       summary_mat <- as.matrix(read.table(summary_file, 
#                                           row.names = row.names, 
#                                           col.names = col.names))
#       
#     }
#   }
#   assign(paste("PAML", "10Tau", paste(toString(IGC.geo), ".0", sep = ""), "2ndTree", "summary", sep = "_"), summary_mat)
# }
# 
# save.image("/Users/xji3/GitFolders/IGCCodonSimulation/All.RData")
```

#### Feb 11 update

```{r}
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",] < 0)
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",] < 0)
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",] < 0)

hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",] < 0],
     main = "lnL difference - local tree 1",
     xlab = "lnL difference")
hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",] < 0],
     main = "lnL difference - local tree 2",
     xlab = "lnL difference")
hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",] < 0],
     main = "lnL difference - local tree 3",
     xlab = "lnL difference")


# OK, more check
sum(PAML_3.0_summary[4, ] < 5e-6 & PAML_3.0_summary[6, ] > 5e-6 )
sum(PAML_3.0_summary[4, ] > 5e-6 & PAML_3.0_summary[6, ] < 5e-6 )
# No asymmetry in the 0 branch length estimates
convert.summary <- function(localTree, summary, vector.names){
  new.summary <- vector("numeric", length(vector.names))
  names(new.summary) <- vector.names
  if (localTree == 1){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- summary["N0_N5"]
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- 0.0
    new.summary["N1_N2"] <- summary["N0_N1"]
    new.summary["N1_castelliiYDR418W"] <- summary["N0_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N1_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N1_N2"]
    new.summary["N3_N4"] <- summary["N2_N3"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N2_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N3_N4"]
    new.summary["N4_mikataeYDR418W"] <- summary["N3_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N4_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N4_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N5_N6"]
    new.summary["N6_castelliiYEL054C"] <- summary["N5_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N6_N7"]
    new.summary["N7_bayanusYEL054C"] <- summary["N6_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N7_N8"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N7_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N8_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N8_N9"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N9_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N9_cerevisiaeYEL054C"]
  
    }
  else if (localTree == 2){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- 0.0
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- summary["N0_N1"]
    new.summary["N1_N2"] <- summary["N1_N2"]
    new.summary["N1_castelliiYDR418W"] <- summary["N1_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N2_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N2_N3"]
    new.summary["N3_N4"] <- summary["N3_N4"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N3_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N4_N5"]
    new.summary["N4_mikataeYDR418W"] <- summary["N4_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N5_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N5_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N0_N6"]
    new.summary["N6_castelliiYEL054C"] <- summary["N0_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N6_N7"]
    new.summary["N7_bayanusYEL054C"] <- summary["N6_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N7_N8"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N7_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N8_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N8_N9"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N9_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N9_cerevisiaeYEL054C"]
    }
  else if (localTree == 3){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- 0.0
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- 0.0
    new.summary["N1_N2"] <- summary["N0_N1"]
    new.summary["N1_castelliiYDR418W"] <- summary["N0_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N1_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N1_N2"]
    new.summary["N3_N4"] <- summary["N2_N3"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N2_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N3_N4"]
    new.summary["N4_mikataeYDR418W"] <- summary["N3_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N4_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N4_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N0_N5"]
    new.summary["N6_castelliiYEL054C"] <- summary["N0_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N5_N6"]
    new.summary["N7_bayanusYEL054C"] <- summary["N5_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N6_N7"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N6_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N7_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N7_N8"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N8_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N8_cerevisiaeYEL054C"]
    }
  else if (localTree == 4){
    new.summary[vector.names] <- summary[vector.names]
    }
  return (new.summary)
  }

for (IGC.geo in IGC.geo.list){
  max.lnL.summary <- NULL
  vector.names = rownames(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = "")))
  for (sim.num in 1:100){
    max.pos <- which.max(c(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_1_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_",paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_2_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_",paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_3_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = ""))["ll", sim.num]))
    if (max.pos < 4){
      new.summary <- convert.summary(max.pos, get(paste("PAML_estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "LocalTree", toString(max.pos), "summary", sep = "_"))[, sim.num], vector.names)
      }
    else{
      new.summary <- get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = ""))[, sim.num]
      }
    max.lnL.summary <- cbind(max.lnL.summary, new.summary)
    }
  row.names(max.lnL.summary) <- row.names(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = "")))
  assign(paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "PAML", "maxlnL", "summary", sep = "_"), max.lnL.summary)
  }

# Now check asymmetry again
# N4_N5
compare.mean.N4.N5.result <- matrix(c(mean(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                      mean(geo_3.0_PAML_maxlnL_summary["N9_N10",]),
                                      mean(geo_3.0_PAML_maxlnL_summary["N4_N5",])/mean(geo_3.0_PAML_maxlnL_summary["N9_N10",]),
                                      mean(PAML_estimatedTau_3.0_1stTree_summary["N4_N5", ]),
                                      mean(PAML_estimatedTau_3.0_1stTree_summary["N9_N10", ]),
                                      mean(PAML_estimatedTau_3.0_1stTree_summary["N4_N5", ])/mean(PAML_estimatedTau_3.0_1stTree_summary["N9_N10", ])),
                                    2, 3, byrow = TRUE)
colnames(compare.mean.N4.N5.result) <- c("paralog1", "paralog2", "paralog1 / paralog2")
rownames(compare.mean.N4.N5.result) <- c("NEW", "old")

compare.sd.N4.N5.result <- matrix(c(sd(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                    sd(geo_3.0_PAML_maxlnL_summary["N9_N10",]),
                                    sd(geo_3.0_PAML_maxlnL_summary["N4_N5",])/sd(geo_3.0_PAML_maxlnL_summary["N9_N10",]),
                                    sd(PAML_estimatedTau_3.0_1stTree_summary["N4_N5", ]),
                                    sd(PAML_estimatedTau_3.0_1stTree_summary["N9_N10", ]),
                                    sd(PAML_estimatedTau_3.0_1stTree_summary["N4_N5", ])/sd(PAML_estimatedTau_3.0_1stTree_summary["N9_N10", ])),
                                  2, 3, byrow = TRUE)
colnames(compare.sd.N4.N5.result) <- c("paralog1", "paralog2", "paralog1 / paralog2")
rownames(compare.sd.N4.N5.result) <- c("NEW", "old")

# N4_mikatae
compare.mean.N4.mikatae.result <- matrix(c(mean(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                           mean(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C",]),
                                           mean(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W",])/mean(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C",]),
                                           mean(PAML_estimatedTau_3.0_1stTree_summary["N4_mikataeYDR418W", ]),
                                           mean(PAML_estimatedTau_3.0_1stTree_summary["N9_mikataeYEL054C", ]),
                                           mean(PAML_estimatedTau_3.0_1stTree_summary["N4_mikataeYDR418W", ])/mean(PAML_estimatedTau_3.0_1stTree_summary["N9_mikataeYEL054C", ])),
                                         2, 3, byrow = TRUE)
colnames(compare.mean.N4.mikatae.result) <- c("paralog1", "paralog2", "paralog1 / paralog2")
rownames(compare.mean.N4.mikatae.result) <- c("NEW", "old")

compare.sd.N4.mikatae.result <- matrix(c(sd(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                         sd(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C",]),
                                         sd(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W",])/sd(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C",]),
                                         sd(PAML_estimatedTau_3.0_1stTree_summary["N4_mikataeYDR418W", ]),
                                         sd(PAML_estimatedTau_3.0_1stTree_summary["N9_mikataeYEL054C", ]),
                                         sd(PAML_estimatedTau_3.0_1stTree_summary["N4_mikataeYDR418W", ])/sd(PAML_estimatedTau_3.0_1stTree_summary["N9_mikataeYEL054C", ])),
                                       2, 3, byrow = TRUE)
colnames(compare.sd.N4.mikatae.result) <- c("paralog1", "paralog2", "paralog1 / paralog2")
rownames(compare.sd.N4.mikatae.result) <- c("NEW", "old")

compare.mean.N4.N5.result
compare.sd.N4.N5.result
compare.mean.N4.mikatae.result
compare.sd.N4.mikatae.result
```

#### Feb 12 update

```{r}
# Now check asymmetry again using best lnL estimates from 4 tree topologies
maxlnL.PAML.omega.mean <- c(mean(geo_3.0_PAML_maxlnL_summary["omega", ]), mean(geo_10.0_PAML_maxlnL_summary["omega", ]),
                            mean(geo_50.0_PAML_maxlnL_summary["omega", ]), mean(geo_100.0_PAML_maxlnL_summary["omega", ]), 
                            mean(geo_500.0_PAML_maxlnL_summary["omega", ]))
maxlnL.PAML.omega.sd <- c(sd(geo_3.0_PAML_maxlnL_summary["omega", ]), sd(geo_10.0_PAML_maxlnL_summary["omega", ]),
                          sd(geo_50.0_PAML_maxlnL_summary["omega", ]), sd(geo_100.0_PAML_maxlnL_summary["omega", ]), 
                          sd(geo_500.0_PAML_maxlnL_summary["omega", ]))

plot(IGC.geo.list, maxlnL.PAML.omega.mean)
abline(h = 1.0)

plot(IGC.geo.list, maxlnL.PAML.omega.sd)

maxlnL.PAML.kappa.mean <- c(mean(geo_3.0_PAML_maxlnL_summary["kappa", ]), mean(geo_10.0_PAML_maxlnL_summary["kappa", ]),
                            mean(geo_50.0_PAML_maxlnL_summary["kappa", ]), mean(geo_100.0_PAML_maxlnL_summary["kappa", ]), 
                            mean(geo_500.0_PAML_maxlnL_summary["kappa", ]))
maxlnL.PAML.kappa.sd <- c(sd(geo_3.0_PAML_maxlnL_summary["kappa", ]), sd(geo_10.0_PAML_maxlnL_summary["kappa", ]),
                          sd(geo_50.0_PAML_maxlnL_summary["kappa", ]), sd(geo_100.0_PAML_maxlnL_summary["kappa", ]), 
                          sd(geo_500.0_PAML_maxlnL_summary["kappa", ]))

plot(IGC.geo.list, maxlnL.PAML.kappa.mean)
abline(h = 8.4043336)

plot(IGC.geo.list, maxlnL.PAML.kappa.sd)
```

Now start to look at branch length estimates

Branch lengths used in simulation:

| Branch | blen |
|--------|------|
|N0_N1:         | 0.0197240946542 |
|N0_kluyveri    | 0.215682181791  |
|N1_N2          | 0.20925129872   |
|N1_castellii   | 0.171684721483  |
|N2_N3          | 0.0257112589202 |
|N2_bayanus     | 0.0266075664688 |
|N3_N4          | 0.0321083243449 |
|N3_kudriavzevii| 0.0853588718458 |
|N4_N5          | 0.024947887926  |
|N4_mikatae     | 0.0566627496729 |
|N5_cerevisiae  | 0.0581451177847 |
|N5_paradoxus   | 0.0218788166581 |

```{r}
# N0_N1
IGC.N0.N1.mean.list <- c(mean(geo_3.0_summary["(N0,N1)", ]), mean(geo_10.0_summary["(N0,N1)", ]),
                         mean(geo_50.0_summary["(N0,N1)", ]), mean(geo_100.0_summary["(N0,N1)", ]),
                         mean(geo_500.0_summary["(N0,N1)", ]))
IGC.N0.N1.sd.list <- c(sd(geo_3.0_summary["(N0,N1)", ]), sd(geo_10.0_summary["(N0,N1)", ]),
                       sd(geo_50.0_summary["(N0,N1)", ]), sd(geo_100.0_summary["(N0,N1)", ]),
                       sd(geo_500.0_summary["(N0,N1)", ]))

PAML.N0.N1.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_N1", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N0_N1", ]))
PAML.N0.N1.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_N1", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N0_N1", ]))
PAML.N0.N1.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_N6", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N0_N6", ]))
PAML.N0.N1.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_N6", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N0_N6", ]))
# N0_kluyveri
IGC.N0.kluyveri.mean.list <- c(mean(geo_3.0_summary["(N0,kluyveri)", ]), mean(geo_10.0_summary["(N0,kluyveri)", ]),
                               mean(geo_50.0_summary["(N0,kluyveri)", ]), mean(geo_100.0_summary["(N0,kluyveri)", ]),
                               mean(geo_500.0_summary["(N0,kluyveri)", ]))
IGC.N0.kluyveri.sd.list <- c(sd(geo_3.0_summary["(N0,kluyveri)", ]), sd(geo_10.0_summary["(N0,kluyveri)", ]),
                             sd(geo_50.0_summary["(N0,kluyveri)", ]), sd(geo_100.0_summary["(N0,kluyveri)", ]),
                             sd(geo_500.0_summary["(N0,kluyveri)", ]))
PAML.N0.kluyveri.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]), 
                                         mean(geo_10.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_50.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_100.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_500.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]))
PAML.N0.kluyveri.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ] ))
# N1_N2
IGC.N1.N2.mean.list <- c(mean(geo_3.0_summary["(N1,N2)", ]), mean(geo_10.0_summary["(N1,N2)", ]),
                         mean(geo_50.0_summary["(N1,N2)", ]), mean(geo_100.0_summary["(N1,N2)", ]),
                         mean(geo_500.0_summary["(N1,N2)", ]))
IGC.N1.N2.sd.list <- c(sd(geo_3.0_summary["(N1,N2)", ]), sd(geo_10.0_summary["(N1,N2)", ]),
                       sd(geo_50.0_summary["(N1,N2)", ]), sd(geo_100.0_summary["(N1,N2)", ]),
                       sd(geo_500.0_summary["(N1,N2)", ]))

PAML.N1.N2.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N1_N2", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N1_N2", ]))
PAML.N1.N2.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N1_N2", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N1_N2", ]))
PAML.N1.N2.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N6_N7", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N6_N7", ]))
PAML.N1.N2.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N6_N7", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N6_N7", ]))

# N1_castellii
IGC.N1.castellii.mean.list <- c(mean(geo_3.0_summary["(N1,castellii)", ]), mean(geo_10.0_summary["(N1,castellii)", ]),
                                mean(geo_50.0_summary["(N1,castellii)", ]), mean(geo_100.0_summary["(N1,castellii)", ]),
                                mean(geo_500.0_summary["(N1,castellii)", ]))
IGC.N1.castellii.sd.list <- c(sd(geo_3.0_summary["(N1,castellii)", ]), sd(geo_10.0_summary["(N1,castellii)", ]),
                              sd(geo_50.0_summary["(N1,castellii)", ]), sd(geo_100.0_summary["(N1,castellii)", ]),
                              sd(geo_500.0_summary["(N1,castellii)", ]))

PAML.N1.castellii.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]))
PAML.N1.castellii.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]))

PAML.N1.castellii.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]))
PAML.N1.castellii.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]))
# N2_N3
IGC.N2.N3.mean.list <- c(mean(geo_3.0_summary["(N2,N3)", ]), mean(geo_10.0_summary["(N2,N3)", ]),
                         mean(geo_50.0_summary["(N2,N3)", ]), mean(geo_100.0_summary["(N2,N3)", ]),
                         mean(geo_500.0_summary["(N2,N3)", ]))
IGC.N2.N3.sd.list <- c(sd(geo_3.0_summary["(N2,N3)", ]), sd(geo_10.0_summary["(N2,N3)", ]),
                       sd(geo_50.0_summary["(N2,N3)", ]), sd(geo_100.0_summary["(N2,N3)", ]),
                       sd(geo_500.0_summary["(N2,N3)", ]))

PAML.N2.N3.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N2_N3", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N2_N3", ]))
PAML.N2.N3.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N2_N3", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N2_N3", ]))
PAML.N2.N3.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N7_N8", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N7_N8", ]))
PAML.N2.N3.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N7_N8", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N7_N8", ]))
# N2_bayanus
IGC.N2.bayanus.mean.list <- c(mean(geo_3.0_summary["(N2,bayanus)", ]), mean(geo_10.0_summary["(N2,bayanus)", ]),
                              mean(geo_50.0_summary["(N2,bayanus)", ]), mean(geo_100.0_summary["(N2,bayanus)", ]),
                              mean(geo_500.0_summary["(N2,bayanus)", ]))
IGC.N2.bayanus.sd.list <- c(sd(geo_3.0_summary["(N2,bayanus)", ]), sd(geo_10.0_summary["(N2,bayanus)", ]),
                            sd(geo_50.0_summary["(N2,bayanus)", ]), sd(geo_100.0_summary["(N2,bayanus)", ]),
                            sd(geo_500.0_summary["(N2,bayanus)", ]))

PAML.N2.bayanus.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]))
PAML.N2.bayanus.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]))
PAML.N2.bayanus.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]))
PAML.N2.bayanus.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]))

# N3_N4
IGC.N3.N4.mean.list <- c(mean(geo_3.0_summary["(N3,N4)", ]), mean(geo_10.0_summary["(N3,N4)", ]),
                         mean(geo_50.0_summary["(N3,N4)", ]), mean(geo_100.0_summary["(N3,N4)", ]),
                         mean(geo_500.0_summary["(N3,N4)", ]))
IGC.N3.N4.sd.list <- c(sd(geo_3.0_summary["(N3,N4)", ]), sd(geo_10.0_summary["(N3,N4)", ]),
                       sd(geo_50.0_summary["(N3,N4)", ]), sd(geo_100.0_summary["(N3,N4)", ]),
                       sd(geo_500.0_summary["(N3,N4)", ]))
PAML.N3.N4.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N3_N4", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N3_N4", ]))
PAML.N3.N4.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N3_N4", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N3_N4", ]))
PAML.N3.N4.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N8_N9", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N8_N9", ]))
PAML.N3.N4.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N8_N9", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N8_N9", ]))
# N3_kudriavzevii
IGC.N3.kudriavzevii.mean.list <- c(mean(geo_3.0_summary["(N3,kudriavzevii)", ]), mean(geo_10.0_summary["(N3,kudriavzevii)", ]),
                                   mean(geo_50.0_summary["(N3,kudriavzevii)", ]), mean(geo_100.0_summary["(N3,kudriavzevii)", ]),
                                   mean(geo_500.0_summary["(N3,kudriavzevii)", ]))
IGC.N3.kudriavzevii.sd.list <- c(sd(geo_3.0_summary["(N3,kudriavzevii)", ]), sd(geo_10.0_summary["(N3,kudriavzevii)", ]),
                                 sd(geo_50.0_summary["(N3,kudriavzevii)", ]), sd(geo_100.0_summary["(N3,kudriavzevii)", ]),
                                 sd(geo_500.0_summary["(N3,kudriavzevii)", ]))
PAML.N3.kudriavzevii.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]), 
                                             mean(geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]))
PAML.N3.kudriavzevii.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]), 
                                           sd(geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]))
PAML.N3.kudriavzevii.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]), 
                                             mean(geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]))
PAML.N3.kudriavzevii.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]), 
                                           sd(geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]))
# N4_N5
IGC.N4.N5.mean.list <- c(mean(geo_3.0_summary["(N4,N5)", ]), mean(geo_10.0_summary["(N4,N5)", ]),
                         mean(geo_50.0_summary["(N4,N5)", ]), mean(geo_100.0_summary["(N4,N5)", ]),
                         mean(geo_500.0_summary["(N4,N5)", ]))
IGC.N4.N5.sd.list <- c(sd(geo_3.0_summary["(N4,N5)", ]), sd(geo_10.0_summary["(N4,N5)", ]),
                       sd(geo_50.0_summary["(N4,N5)", ]), sd(geo_100.0_summary["(N4,N5)", ]),
                       sd(geo_500.0_summary["(N4,N5)", ]))
PAML.N4.N5.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N4_N5", ]))
PAML.N4.N5.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N4_N5", ]))
PAML.N4.N5.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N9_N10", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N9_N10", ]))
PAML.N4.N5.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N9_N10", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N9_N10", ]))
# N4_mikatae
IGC.N4.mikatae.mean.list <- c(mean(geo_3.0_summary["(N4,mikatae)", ]), mean(geo_10.0_summary["(N4,mikatae)", ]),
                              mean(geo_50.0_summary["(N4,mikatae)", ]), mean(geo_100.0_summary["(N4,mikatae)", ]),
                              mean(geo_500.0_summary["(N4,mikatae)", ]))
IGC.N4.mikatae.sd.list <- c(sd(geo_3.0_summary["(N4,mikatae)", ]), sd(geo_10.0_summary["(N4,mikatae)", ]),
                            sd(geo_50.0_summary["(N4,mikatae)", ]), sd(geo_100.0_summary["(N4,mikatae)", ]),
                            sd(geo_500.0_summary["(N4,mikatae)", ]))
PAML.N4.mikatae.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]))
PAML.N4.mikatae.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]))
PAML.N4.mikatae.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]))
PAML.N4.mikatae.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]))
# N5_cerevisiae
IGC.N5.cerevisiae.mean.list <- c(mean(geo_3.0_summary["(N5,cerevisiae)", ]), mean(geo_10.0_summary["(N5,cerevisiae)", ]),
                                 mean(geo_50.0_summary["(N5,cerevisiae)", ]), mean(geo_100.0_summary["(N5,cerevisiae)", ]),
                                 mean(geo_500.0_summary["(N5,cerevisiae)", ]))
IGC.N5.cerevisiae.sd.list <- c(sd(geo_3.0_summary["(N5,cerevisiae)", ]), sd(geo_10.0_summary["(N5,cerevisiae)", ]),
                               sd(geo_50.0_summary["(N5,cerevisiae)", ]), sd(geo_100.0_summary["(N5,cerevisiae)", ]),
                               sd(geo_500.0_summary["(N5,cerevisiae)", ]))
PAML.N5.cerevisiae.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]), 
                                           mean(geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]))
PAML.N5.cerevisiae.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]))
PAML.N5.cerevisiae.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]), 
                                           mean(geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]))
PAML.N5.cerevisiae.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]))
# N5_paradoxus
IGC.N5.paradoxus.mean.list <- c(mean(geo_3.0_summary["(N5,paradoxus)", ]), mean(geo_10.0_summary["(N5,paradoxus)", ]),
                                mean(geo_50.0_summary["(N5,paradoxus)", ]), mean(geo_100.0_summary["(N5,paradoxus)", ]),
                                mean(geo_500.0_summary["(N5,paradoxus)", ]))
IGC.N5.paradoxus.sd.list <- c(sd(geo_3.0_summary["(N5,paradoxus)", ]), sd(geo_10.0_summary["(N5,paradoxus)", ]),
                              sd(geo_50.0_summary["(N5,paradoxus)", ]), sd(geo_100.0_summary["(N5,paradoxus)", ]),
                              sd(geo_500.0_summary["(N5,paradoxus)", ]))
PAML.N5.paradoxus.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]))
PAML.N5.paradoxus.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]))
PAML.N5.paradoxus.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]))
PAML.N5.paradoxus.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]))
```

Now plot same branch length estimates from each paralog in paml results and posterior branch length from IGC + MG94 model

```{r}
# N0_N1
matplot(IGC.geo.list, cbind(PAML.N0.N1.maxlnL.paralog1.mean.list, PAML.N0.N1.maxlnL.paralog2.mean.list, mean.post.N0.N1.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N0.N1 estimate")
abline(h = 0.0197240946542)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N0.N1.maxlnL.paralog1.sd.list, PAML.N0.N1.maxlnL.paralog2.sd.list, sd.post.N0.N1.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N0.N1 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N0_kluyveri
matplot(IGC.geo.list, cbind(PAML.N0.kluyveri.maxlnL.paralog1.mean.list, mean.post.N0.kluyveri.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N0.kluyveri estimate")
abline(h = 0.215682181791)
legend("right", legend = c("paralog1", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N0.kluyveri.maxlnL.paralog1.sd.list, sd.post.N0.kluyveri.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N0.kluyveri estimate")
legend("right", legend = c("paralog1", "posterior IGC"), col = 1:3, pch = 1)

# N1_N2
matplot(IGC.geo.list, cbind(PAML.N1.N2.maxlnL.paralog1.mean.list, PAML.N1.N2.maxlnL.paralog2.mean.list, mean.post.N1.N2.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N1.N2 estimate")
abline(h = 0.20925129872)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N1.N2.maxlnL.paralog1.sd.list, PAML.N1.N2.maxlnL.paralog2.sd.list, sd.post.N1.N2.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N1.N2 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N1_castellii
matplot(IGC.geo.list, cbind(PAML.N1.castellii.maxlnL.paralog1.mean.list, PAML.N1.castellii.maxlnL.paralog2.mean.list, mean.post.N1.castellii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N1.castellii estimate")
abline(h = 0.171684721483)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N1.castellii.maxlnL.paralog1.sd.list, PAML.N1.castellii.maxlnL.paralog2.sd.list, sd.post.N1.castellii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N1.castellii estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N2_N3
matplot(IGC.geo.list, cbind(PAML.N2.N3.maxlnL.paralog1.mean.list, PAML.N2.N3.maxlnL.paralog2.mean.list, mean.post.N2.N3.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N2.N3 estimate")
abline(h = 0.0257112589202)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N2.N3.maxlnL.paralog1.sd.list, PAML.N2.N3.maxlnL.paralog2.sd.list, sd.post.N2.N3.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N2.N3 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N2_bayanus
matplot(IGC.geo.list, cbind(PAML.N2.bayanus.maxlnL.paralog1.mean.list, PAML.N2.bayanus.maxlnL.paralog2.mean.list, mean.post.N2.bayanus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N2.bayanus estimate")
abline(h = 0.0266075664688)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N2.bayanus.maxlnL.paralog1.sd.list, PAML.N2.bayanus.maxlnL.paralog2.sd.list, sd.post.N2.bayanus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N2.bayanus estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N3_N4
matplot(IGC.geo.list, cbind(PAML.N3.N4.maxlnL.paralog1.mean.list, PAML.N3.N4.maxlnL.paralog2.mean.list, mean.post.N3.N4.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N3.N4 estimate")
abline(h = 0.0321083243449)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N3.N4.maxlnL.paralog1.sd.list, PAML.N3.N4.maxlnL.paralog2.sd.list, sd.post.N3.N4.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N3.N4 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N3_kudriavzevii
matplot(IGC.geo.list, cbind(PAML.N3.kudriavzevii.maxlnL.paralog1.mean.list, PAML.N3.kudriavzevii.maxlnL.paralog2.mean.list, mean.post.N3.kudriavzevii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N3.kudriavzevii estimate")
abline(h = 0.0853588718458)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N3.kudriavzevii.maxlnL.paralog1.sd.list, PAML.N3.kudriavzevii.maxlnL.paralog2.sd.list, sd.post.N3.kudriavzevii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N3.kudriavzevii estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N4_N5
matplot(IGC.geo.list, cbind(PAML.N4.N5.maxlnL.paralog1.mean.list, PAML.N4.N5.maxlnL.paralog2.mean.list, mean.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.N5 estimate")
abline(h = 0.024947887926)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.N5.maxlnL.paralog1.sd.list, PAML.N4.N5.maxlnL.paralog2.sd.list, sd.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.N5 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N4_mikatae
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.maxlnL.paralog1.mean.list, PAML.N4.mikatae.maxlnL.paralog2.mean.list, mean.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.mikatae estimate")
abline(h = 0.0566627496729)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.maxlnL.paralog1.sd.list, PAML.N4.mikatae.maxlnL.paralog2.sd.list, sd.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.mikatae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N5_cerevisiae
matplot(IGC.geo.list, cbind(PAML.N5.cerevisiae.maxlnL.paralog1.mean.list, PAML.N5.cerevisiae.maxlnL.paralog2.mean.list, mean.post.N5.cerevisiae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N5.cerevisiae estimate")
abline(h = 0.0581451177847)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N5.cerevisiae.maxlnL.paralog1.sd.list, PAML.N5.cerevisiae.maxlnL.paralog2.sd.list, sd.post.N5.cerevisiae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N5.cerevisiae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N5_paradoxus
matplot(IGC.geo.list, cbind(PAML.N5.paradoxus.maxlnL.paralog1.mean.list, PAML.N5.paradoxus.maxlnL.paralog2.mean.list, mean.post.N5.paradoxus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N5.paradoxus estimate")
abline(h = 0.0218788166581)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N5.paradoxus.maxlnL.paralog1.sd.list, PAML.N5.paradoxus.maxlnL.paralog2.sd.list, sd.post.N5.paradoxus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N5.paradoxus estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

```

#### Feb 10 update

```{r}
# Re-examine N4_N5, N4_mikatae
IGC.geo.list <- c(3.0, 10.0, 50.0, 100.0, 500.0)

# N4_N5
non.zero.PAML.N4.N5.paralog1.mean.list <- c(mean(PAML_3.0_summary["N4_N5", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                            mean(PAML_10.0_summary["N4_N5", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                            mean(PAML_50.0_summary["N4_N5", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                            mean(PAML_100.0_summary["N4_N5", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                            mean(PAML_500.0_summary["N4_N5", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.N5.paralog1.sd.list <- c(sd(PAML_3.0_summary["N4_N5", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                          sd(PAML_10.0_summary["N4_N5", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                          sd(PAML_50.0_summary["N4_N5", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                          sd(PAML_100.0_summary["N4_N5", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                          sd(PAML_500.0_summary["N4_N5", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.N5.paralog2.mean.list <- c(mean(PAML_3.0_summary["N9_N10", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                            mean(PAML_10.0_summary["N9_N10", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                            mean(PAML_50.0_summary["N9_N10", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                            mean(PAML_100.0_summary["N9_N10", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                            mean(PAML_500.0_summary["N9_N10", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.N5.paralog2.sd.list <- c(sd(PAML_3.0_summary["N9_N10", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                          sd(PAML_10.0_summary["N9_N10", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                          sd(PAML_50.0_summary["N9_N10", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                          sd(PAML_100.0_summary["N9_N10", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                          sd(PAML_500.0_summary["N9_N10", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
# N4_mikatae
non.zero.PAML.N4.mikatae.paralog1.mean.list <- c(mean(PAML_3.0_summary["N4_mikataeYDR418W", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                                 mean(PAML_10.0_summary["N4_mikataeYDR418W", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_50.0_summary["N4_mikataeYDR418W", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_100.0_summary["N4_mikataeYDR418W", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_500.0_summary["N4_mikataeYDR418W", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.mikatae.paralog1.sd.list <- c(sd(PAML_3.0_summary["N4_mikataeYDR418W", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                               sd(PAML_10.0_summary["N4_mikataeYDR418W", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                               sd(PAML_50.0_summary["N4_mikataeYDR418W", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                               sd(PAML_100.0_summary["N4_mikataeYDR418W", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                               sd(PAML_500.0_summary["N4_mikataeYDR418W", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.mikatae.paralog2.mean.list <- c(mean(PAML_3.0_summary["N9_mikataeYEL054C", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                                 mean(PAML_10.0_summary["N9_mikataeYEL054C", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_50.0_summary["N9_mikataeYEL054C", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_100.0_summary["N9_mikataeYEL054C", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                                 mean(PAML_500.0_summary["N9_mikataeYEL054C", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))
non.zero.PAML.N4.mikatae.paralog2.sd.list <- c(sd(PAML_3.0_summary["N9_mikataeYEL054C", (PAML_3.0_summary[4, ] > 1e-5 & PAML_3.0_summary[6,] > 1e-5)]), 
                                               sd(PAML_10.0_summary["N9_mikataeYEL054C", (PAML_10.0_summary[4, ] > 1e-5 & PAML_10.0_summary[6,] > 1e-5)]),
                                               sd(PAML_50.0_summary["N9_mikataeYEL054C", (PAML_50.0_summary[4, ] > 1e-5 & PAML_50.0_summary[6,] > 1e-5)]),
                                               sd(PAML_100.0_summary["N9_mikataeYEL054C", (PAML_100.0_summary[4, ] > 1e-5 & PAML_100.0_summary[6,] > 1e-5)]),
                                               sd(PAML_500.0_summary["N9_mikataeYEL054C", (PAML_500.0_summary[4, ] > 1e-5 & PAML_500.0_summary[6,] > 1e-5)]))

# N4_N5
par(mfrow = c(2, 2))
matplot(IGC.geo.list, cbind(non.zero.PAML.N4.N5.paralog1.mean.list, non.zero.PAML.N4.N5.paralog2.mean.list, mean.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean non.zero N4.N5 estimate")
abline(h = 0.024947887926)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(non.zero.PAML.N4.N5.paralog1.sd.list, non.zero.PAML.N4.N5.paralog2.sd.list, sd.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd non.zero N4.N5 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N4_N5
matplot(IGC.geo.list, cbind(PAML.N4.N5.paralog1.mean.list, PAML.N4.N5.paralog2.mean.list, mean.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.N5 estimate")
abline(h = 0.024947887926)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.N5.paralog1.sd.list, PAML.N4.N5.paralog2.sd.list, sd.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.N5 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)


par(mfrow = c(2, 2))
# N4_mikatae
matplot(IGC.geo.list, cbind(non.zero.PAML.N4.mikatae.paralog1.mean.list, non.zero.PAML.N4.mikatae.paralog2.mean.list, mean.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean non.zero N4.mikatae estimate")
abline(h = 0.0566627496729)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(non.zero.PAML.N4.mikatae.paralog1.sd.list, non.zero.PAML.N4.mikatae.paralog2.sd.list, sd.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd non.zero N4.mikatae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
# N4_mikatae
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.paralog1.mean.list, PAML.N4.mikatae.paralog2.mean.list, mean.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.mikatae estimate")
abline(h = 0.0566627496729)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.paralog1.sd.list, PAML.N4.mikatae.paralog2.sd.list, sd.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.mikatae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)



```

#### Feb 5 update

Check PAML estimate of two same tree topologies but different order of taxa

```{r}
# Simulation using estimated Tau value of 1.409408
# Look at difference of each estimate (Tree 1 - Tree 2)

# log likelihood
summary(PAML_estimatedTau_3.0_1stTree_summary["ll", ] - PAML_estimatedTau_3.0_2ndTree_summary["ll", ])
sd(PAML_estimatedTau_3.0_1stTree_summary["ll", ] - PAML_estimatedTau_3.0_2ndTree_summary["ll", ])
# kappa
summary(PAML_estimatedTau_3.0_1stTree_summary["kappa", ] - PAML_estimatedTau_3.0_2ndTree_summary["kappa", ])
sd(PAML_estimatedTau_3.0_1stTree_summary["kappa", ] - PAML_estimatedTau_3.0_2ndTree_summary["kappa", ])
# omega
summary(PAML_estimatedTau_3.0_1stTree_summary["omega", ] - PAML_estimatedTau_3.0_2ndTree_summary["omega", ])
sd(PAML_estimatedTau_3.0_1stTree_summary["omega", ] - PAML_estimatedTau_3.0_2ndTree_summary["omega", ])
# N0_kluyveriYDR418W
summary(PAML_estimatedTau_3.0_1stTree_summary["N0_kluyveriYDR418W", ] - PAML_estimatedTau_3.0_2ndTree_summary["N0_kluyveriYDR418W", ])
sd(PAML_estimatedTau_3.0_1stTree_summary["N0_kluyveriYDR418W", ] - PAML_estimatedTau_3.0_2ndTree_summary["N0_kluyveriYDR418W", ])
# N0_N1
summary(PAML_estimatedTau_3.0_1stTree_summary["N0_N1", ] - PAML_estimatedTau_3.0_2ndTree_summary["N0_N6", ])
sd(PAML_estimatedTau_3.0_1stTree_summary["N0_N1", ] - PAML_estimatedTau_3.0_2ndTree_summary["N0_N6", ])
```

There seems no difference between two different tree representations

Now check PAML results on simulation with 10*Tau 

```{r}
# Simulation using 10 * Tau value of 1.409408 * 10 = 14.09408
# Look at difference of each estimate (Tree 1 - Tree 2)

# log likelihood
summary(PAML_10Tau_3.0_1stTree_summary["ll", ] - PAML_10Tau_3.0_2ndTree_summary["ll", ])
sd(PAML_10Tau_3.0_1stTree_summary["ll", ] - PAML_10Tau_3.0_2ndTree_summary["ll", ])
hist(PAML_10Tau_3.0_1stTree_summary["ll", ] - PAML_10Tau_3.0_2ndTree_summary["ll", ])
# kappa
summary(PAML_10Tau_3.0_1stTree_summary["kappa", ] - PAML_10Tau_3.0_2ndTree_summary["kappa", ])
sd(PAML_10Tau_3.0_1stTree_summary["kappa", ] - PAML_10Tau_3.0_2ndTree_summary["kappa", ])
# omega
summary(PAML_10Tau_3.0_1stTree_summary["omega", ] - PAML_10Tau_3.0_2ndTree_summary["omega", ])
sd(PAML_10Tau_3.0_1stTree_summary["omega", ] - PAML_10Tau_3.0_2ndTree_summary["omega", ])
# N0_kluyveriYDR418W
summary(PAML_10Tau_3.0_1stTree_summary["N0_kluyveriYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N0_kluyveriYDR418W", ])
sd(PAML_10Tau_3.0_1stTree_summary["N0_kluyveriYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N0_kluyveriYDR418W", ])
# N0_N1
summary(PAML_10Tau_3.0_1stTree_summary["N0_N1", ] - PAML_10Tau_3.0_2ndTree_summary["N0_N6", ])
sd(PAML_10Tau_3.0_1stTree_summary["N0_N1", ] - PAML_10Tau_3.0_2ndTree_summary["N0_N6", ])
# N1_N2
summary(PAML_10Tau_3.0_1stTree_summary["N1_N2", ] - PAML_10Tau_3.0_2ndTree_summary["N6_N7", ])
sd(PAML_10Tau_3.0_1stTree_summary["N1_N2", ] - PAML_10Tau_3.0_2ndTree_summary["N6_N7", ])
hist(PAML_10Tau_3.0_1stTree_summary["N1_N2", ] - PAML_10Tau_3.0_2ndTree_summary["N6_N7", ])
# N1_castelliiYDR418W
summary(PAML_10Tau_3.0_1stTree_summary["N1_castelliiYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N6_castelliiYDR418W", ])
sd(PAML_10Tau_3.0_1stTree_summary["N1_castelliiYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N6_castelliiYDR418W", ])
hist(PAML_10Tau_3.0_1stTree_summary["N1_castelliiYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N6_castelliiYDR418W", ])
# N2_N3
summary(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
sd(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
hist(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
# N2_N3
summary(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
sd(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
hist(PAML_10Tau_3.0_1stTree_summary["N2_N3", ] - PAML_10Tau_3.0_2ndTree_summary["N7_N8", ])
# N2_bayanusYDR418W
summary(PAML_10Tau_3.0_1stTree_summary["N2_bayanusYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N7_bayanusYDR418W", ])
sd(PAML_10Tau_3.0_1stTree_summary["N2_bayanusYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N7_bayanusYDR418W", ])
hist(PAML_10Tau_3.0_1stTree_summary["N2_bayanusYDR418W", ] - PAML_10Tau_3.0_2ndTree_summary["N7_bayanusYDR418W", ])

```
Now start to check branches ratio of subtree branches of paralog 1 over paralog 2 ratios

```{r}
# N0_N1
target <- PAML_3.0_summary["N0_N1", ] / PAML_3.0_summary["N0_N6", ]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
target <- PAML_3.0_summary["N1_N2", ] / PAML_3.0_summary["N6_N7", ]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
target <- PAML_3.0_summary["N1_castelliiYDR418W", ] / PAML_3.0_summary["N6_castelliiYEL054C", ]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
target <- PAML_3.0_summary["N2_N3", ] / PAML_3.0_summary["N7_N8", ]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
target <- PAML_3.0_summary["N2_bayanusYDR418W", ] / PAML_3.0_summary["N7_bayanusYEL054C", ]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
target <- PAML_3.0_summary["N3_N4", ] / PAML_3.0_summary["N8_N9", ]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
target <- PAML_3.0_summary["N3_kudriavzeviiYDR418W", ] / PAML_3.0_summary["N8_kudriavzeviiYEL054C", ]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
target <- PAML_3.0_summary["N4_N5", ] / PAML_3.0_summary["N9_N10", ]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
target <- PAML_3.0_summary["N4_mikataeYDR418W", ] / PAML_3.0_summary["N9_mikataeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
target <- PAML_3.0_summary["N5_paradoxusYDR418W", ] / PAML_3.0_summary["N10_paradoxusYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
target <- PAML_3.0_summary["N5_cerevisiaeYDR418W", ] / PAML_3.0_summary["N10_cerevisiaeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)

# N0_N1
target <- PAML_10.0_summary["N0_N1", ] / PAML_10.0_summary["N0_N6", ]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
target <- PAML_10.0_summary["N1_N2", ] / PAML_10.0_summary["N6_N7", ]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
target <- PAML_10.0_summary["N1_castelliiYDR418W", ] / PAML_10.0_summary["N6_castelliiYEL054C", ]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
target <- PAML_10.0_summary["N2_N3", ] / PAML_10.0_summary["N7_N8", ]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
target <- PAML_10.0_summary["N2_bayanusYDR418W", ] / PAML_10.0_summary["N7_bayanusYEL054C", ]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
target <- PAML_10.0_summary["N3_N4", ] / PAML_10.0_summary["N8_N9", ]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
target <- PAML_10.0_summary["N3_kudriavzeviiYDR418W", ] / PAML_10.0_summary["N8_kudriavzeviiYEL054C", ]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
target <- PAML_10.0_summary["N4_N5", ] / PAML_10.0_summary["N9_N10", ]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
target <- PAML_10.0_summary["N4_mikataeYDR418W", ] / PAML_10.0_summary["N9_mikataeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
target <- PAML_10.0_summary["N5_paradoxusYDR418W", ] / PAML_10.0_summary["N10_paradoxusYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
target <- PAML_10.0_summary["N5_cerevisiaeYDR418W", ] / PAML_10.0_summary["N10_cerevisiaeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)

# N0_N1
target <- PAML_50.0_summary["N0_N1", ] / PAML_50.0_summary["N0_N6", ]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
target <- PAML_50.0_summary["N1_N2", ] / PAML_50.0_summary["N6_N7", ]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
target <- PAML_50.0_summary["N1_castelliiYDR418W", ] / PAML_50.0_summary["N6_castelliiYEL054C", ]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
target <- PAML_50.0_summary["N2_N3", ] / PAML_50.0_summary["N7_N8", ]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
target <- PAML_50.0_summary["N2_bayanusYDR418W", ] / PAML_50.0_summary["N7_bayanusYEL054C", ]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
target <- PAML_50.0_summary["N3_N4", ] / PAML_50.0_summary["N8_N9", ]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
target <- PAML_50.0_summary["N3_kudriavzeviiYDR418W", ] / PAML_50.0_summary["N8_kudriavzeviiYEL054C", ]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
target <- PAML_50.0_summary["N4_N5", ] / PAML_50.0_summary["N9_N10", ]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
target <- PAML_50.0_summary["N4_mikataeYDR418W", ] / PAML_50.0_summary["N9_mikataeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
target <- PAML_50.0_summary["N5_paradoxusYDR418W", ] / PAML_50.0_summary["N10_paradoxusYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
target <- PAML_50.0_summary["N5_cerevisiaeYDR418W", ] / PAML_50.0_summary["N10_cerevisiaeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)
# N0_N1
target <- PAML_100.0_summary["N0_N1", ] / PAML_100.0_summary["N0_N6", ]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
target <- PAML_100.0_summary["N1_N2", ] / PAML_100.0_summary["N6_N7", ]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
target <- PAML_100.0_summary["N1_castelliiYDR418W", ] / PAML_100.0_summary["N6_castelliiYEL054C", ]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
target <- PAML_100.0_summary["N2_N3", ] / PAML_100.0_summary["N7_N8", ]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
target <- PAML_100.0_summary["N2_bayanusYDR418W", ] / PAML_100.0_summary["N7_bayanusYEL054C", ]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
target <- PAML_100.0_summary["N3_N4", ] / PAML_100.0_summary["N8_N9", ]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
target <- PAML_100.0_summary["N3_kudriavzeviiYDR418W", ] / PAML_100.0_summary["N8_kudriavzeviiYEL054C", ]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
target <- PAML_100.0_summary["N4_N5", ] / PAML_100.0_summary["N9_N10", ]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
target <- PAML_100.0_summary["N4_mikataeYDR418W", ] / PAML_100.0_summary["N9_mikataeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
target <- PAML_100.0_summary["N5_paradoxusYDR418W", ] / PAML_100.0_summary["N10_paradoxusYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
target <- PAML_100.0_summary["N5_cerevisiaeYDR418W", ] / PAML_100.0_summary["N10_cerevisiaeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)
# N0_N1
target <- PAML_500.0_summary["N0_N1", ] / PAML_500.0_summary["N0_N6", ]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
target <- PAML_500.0_summary["N1_N2", ] / PAML_500.0_summary["N6_N7", ]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
target <- PAML_500.0_summary["N1_castelliiYDR418W", ] / PAML_500.0_summary["N6_castelliiYEL054C", ]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
target <- PAML_500.0_summary["N2_N3", ] / PAML_500.0_summary["N7_N8", ]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
target <- PAML_500.0_summary["N2_bayanusYDR418W", ] / PAML_500.0_summary["N7_bayanusYEL054C", ]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
target <- PAML_500.0_summary["N3_N4", ] / PAML_500.0_summary["N8_N9", ]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
target <- PAML_500.0_summary["N3_kudriavzeviiYDR418W", ] / PAML_500.0_summary["N8_kudriavzeviiYEL054C", ]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
target <- PAML_500.0_summary["N4_N5", ] / PAML_500.0_summary["N9_N10", ]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
target <- PAML_500.0_summary["N4_mikataeYDR418W", ] / PAML_500.0_summary["N9_mikataeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
target <- PAML_500.0_summary["N5_paradoxusYDR418W", ] / PAML_500.0_summary["N10_paradoxusYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
target <- PAML_500.0_summary["N5_cerevisiaeYDR418W", ] / PAML_500.0_summary["N10_cerevisiaeYEL054C", ]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)


```