---
title: "IGCCodonSimPAMLsummary"
output: html_document
---


Load data from All.RData

```{r}
rm(list=ls())  # clean up workspace
load("/Users/Xiang/GitFolders/IGCCodonSimulation/All.RData")
## try http:// if https:// URLs are not supported
#source("https://bioconductor.org/biocLite.R")
#biocLite("ggtree")
#library("ggtree")
library("ape")

IGC.geo.list <- c(3.0, 10.0, 50.0, 100.0, 500.0)
for (IGC.geo in IGC.geo.list){
  PAML.local.tree.1 <- NULL
  PAML.local.tree.2 <- NULL
  PAML.local.tree.3 <- NULL
  tree.local.1 <- read.tree(file = paste( "/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_0/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_0_localTree_1_codeml_est.newick", sep = ""))
  edge.local.1 <- tree.local.1$edge
  check.1 <- TRUE
  tree.local.2 <- read.tree(file = paste( "/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_0/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_0_localTree_2_codeml_est.newick", sep = ""))
  edge.local.2 <- tree.local.2$edge
  check.2 <- TRUE
  tree.local.3 <- read.tree(file = paste( "/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_0/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_0_localTree_3_codeml_est.newick", sep = ""))
  edge.local.3 <- tree.local.3$edge
  check.3 <- TRUE
  
  for (sim.num in 0:99){
    newick.tree.file <- paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_", toString(sim.num),"/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_", toString(sim.num), "_localTree_1_codeml_est.newick", sep = "") 
    tree.local.1 <- read.tree(file = newick.tree.file)
    check.1 <- check.1 & all(edge.local.1 == tree.local.1$edge)
    PAML.local.tree.1 <- cbind(PAML.local.tree.1, tree.local.1$edge.length)
    
    newick.tree.file <- paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_", toString(sim.num),"/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_", toString(sim.num), "_localTree_2_codeml_est.newick", sep = "") 
    tree.local.2 <- read.tree(file = newick.tree.file)
    check.2 <- check.2 & all(edge.local.2 == tree.local.2$edge)
    PAML.local.tree.2 <- cbind(PAML.local.tree.2, tree.local.2$edge.length)
    
    newick.tree.file <- paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_", toString(sim.num),"/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_", toString(sim.num), "_localTree_3_codeml_est.newick", sep = "") 
    tree.local.3 <- read.tree(file = newick.tree.file)
    check.3 <- check.3 & all(edge.local.3 == tree.local.3$edge)
    PAML.local.tree.3 <- cbind(PAML.local.tree.3, tree.local.3$edge.length)
  }
  
  # Now assign rownames
  node.names.1 <- c("cerevisiaeYDR418W", "paradoxusYDR418W", "mikataeYDR418W", "kudriavzeviiYDR418W",
                    "bayanusYDR418W", "castelliiYDR418W", "cerevisiaeYEL054C", "paradoxusYEL054C", 
                    "mikataeYEL054C", "kudriavzeviiYEL054C", "bayanusYEL054C", "castelliiYEL054C",
                    "kluyveriYDR418W",
                    "N0", "N1", "N2", "N3", "N4", "N5",
                    "N6", "N7", "N8", "N9")
  node.names.2 <- c("cerevisiaeYDR418W", "paradoxusYDR418W", "mikataeYDR418W", "kudriavzeviiYDR418W",
                    "bayanusYDR418W", "castelliiYDR418W", "cerevisiaeYEL054C", "paradoxusYEL054C", 
                    "mikataeYEL054C", "kudriavzeviiYEL054C", "bayanusYEL054C", "castelliiYEL054C",
                    "kluyveriYDR418W",
                    "N0", "N1", "N2", "N3", "N4", "N5",
                    "N6", "N7", "N8", "N9")
  node.names.3 <- c("cerevisiaeYDR418W", "paradoxusYDR418W", "mikataeYDR418W", "kudriavzeviiYDR418W",
                    "bayanusYDR418W", "castelliiYDR418W", "cerevisiaeYEL054C", "paradoxusYEL054C", 
                    "mikataeYEL054C", "kudriavzeviiYEL054C", "bayanusYEL054C", "castelliiYEL054C",
                    "kluyveriYDR418W",
                    "N0", "N1", "N2", "N3", "N4", "N5", "N6",
                    "N7", "N8")
  local.row.names.1 <- NULL
  for (i in 1:dim(edge.local.1)[1]){
    local.row.names.1 <- c(local.row.names.1, paste(node.names.1[edge.local.1[i, 1]], node.names.1[edge.local.1[i, 2]], sep = "_"))
  }
  local.row.names.2 <- NULL
  for (i in 1:dim(edge.local.2)[1]){
    local.row.names.2 <- c(local.row.names.2, paste(node.names.2[edge.local.2[i, 1]], node.names.2[edge.local.2[i, 2]], sep = "_"))
  }
  local.row.names.3 <- NULL
  for (i in 1:dim(edge.local.3)[1]){
    local.row.names.3 <- c(local.row.names.3, paste(node.names.3[edge.local.3[i, 1]], node.names.3[edge.local.3[i, 2]], sep = "_"))
  }
  rownames(PAML.local.tree.1) <- local.row.names.1
  rownames(PAML.local.tree.2) <- local.row.names.2
  rownames(PAML.local.tree.3) <- local.row.names.3
  assign(paste("ape_paml_localTree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""), PAML.local.tree.1)
  assign(paste("ape_paml_localTree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""), PAML.local.tree.2)
  assign(paste("ape_paml_localTree_3_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""), PAML.local.tree.3)
}
```

Now load in two representations of the correct tree topology

```{r}
for (IGC.geo in IGC.geo.list){
  PAML.tree.1 <- NULL
  PAML.tree.2 <- NULL
  
  tree.1 <- read.tree(file = paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_0/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_0_codeml_tree1_est.newick", sep = ""))
  edge.1 <- tree.1$edge
  check.1 <- TRUE
  
  tree.2 <- read.tree(file = paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_0/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_0_codeml_tree2_est.newick", sep = ""))
  edge.2 <- tree.2$edge
  check.2 <- TRUE
  
  for (sim.num in 0:99){
    newick.tree.file <- paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_", toString(sim.num),"/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_", toString(sim.num), "_codeml_tree1_est.newick", sep = "") 
    tree.1 <- read.tree(file = newick.tree.file)
    check.1 <- check.1 & all(edge.1 == tree.1$edge)
    PAML.tree.1 <- cbind(PAML.tree.1, tree.1$edge.length)
    
    newick.tree.file <- paste("/Users/Xiang/GitFolders/IGCCodonSimulation/YDR418W_YEL054C_estimatedTau/IGCgeo_", toString(IGC.geo), ".0/sim_", toString(sim.num),"/unrooted_MG94_geo_", toString(IGC.geo), ".0_Sim_", toString(sim.num), "_codeml_tree2_est.newick", sep = "") 
    tree.2 <- read.tree(file = newick.tree.file)
    check.2 <- check.2 & all(edge.2 == tree.2$edge)
    PAML.tree.2 <- cbind(PAML.tree.2, tree.2$edge.length)
  }
  # Now assign rownames
  node.names.1 <- c("cerevisiaeYDR418W", "paradoxusYDR418W", "mikataeYDR418W", "kudriavzeviiYDR418W",
                    "bayanusYDR418W", "castelliiYDR418W", "cerevisiaeYEL054C", "paradoxusYEL054C", 
                    "mikataeYEL054C", "kudriavzeviiYEL054C", "bayanusYEL054C", "castelliiYEL054C",
                    "kluyveriYDR418W",
                    "N0", "N1", "N2", "N3", "N4", "N5",
                    "N6", "N7", "N8", "N9", "N10")
  node.names.2 <- c("kluyveriYDR418W", "castelliiYEL054C", "bayanusYEL054C", "kudriavzeviiYEL054C",
                    "mikataeYEL054C","cerevisiaeYEL054C", "paradoxusYEL054C", "castelliiYDR418W",
                    "bayanusYDR418W", "kudriavzeviiYDR418W", "mikataeYDR418W", "cerevisiaeYDR418W", 
                    "paradoxusYDR418W",
                    "N0", 
                    "N1", "N2", "N3", "N4", "N5",
                    "N6", "N7", "N8", "N9", "N10")
  
  row.names.1 <- NULL
  for (i in 1:dim(edge.1)[1]){
    row.names.1 <- c(row.names.1, paste(node.names.1[edge.1[i, 1]], node.names.1[edge.1[i, 2]], sep = "_"))
  }
  row.names.2 <- NULL
  for (i in 1:dim(edge.2)[1]){
    row.names.2 <- c(row.names.2, paste(node.names.2[edge.2[i, 1]], node.names.2[edge.2[i, 2]], sep = "_"))
  }
  rownames(PAML.tree.1) <- row.names.1
  rownames(PAML.tree.2) <- row.names.2
  assign(paste("ape_paml_Tree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""), PAML.tree.1)
  assign(paste("ape_paml_Tree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""), PAML.tree.2)
}
# save.image("/Users/Xiang/GitFolders/IGCCodonSimulation/All.RData")
```

Now, check if two parsers give same branch length estimates

```{r}
for (IGC.geo in IGC.geo.list){
  print(paste("IGC.geo = ", toString(IGC.geo)))
  # Local trees
  print(sum(abs(get(paste("ape_paml_localTree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = "")) - get(paste("PAML_estimatedTau_", toString(IGC.geo), ".0_LocalTree_1_summary", sep = ""))[rownames(get(paste("ape_paml_localTree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""))),])))
  print(sum(abs(get(paste("ape_paml_localTree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = "")) - get(paste("PAML_estimatedTau_", toString(IGC.geo), ".0_LocalTree_2_summary", sep = ""))[rownames(get(paste("ape_paml_localTree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""))),])))
  print(sum(abs(get(paste("ape_paml_localTree_3_geo_", toString(IGC.geo), ".0_blen_summary", sep = "")) - get(paste("PAML_estimatedTau_", toString(IGC.geo), ".0_LocalTree_3_summary", sep = ""))[rownames(get(paste("ape_paml_localTree_3_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""))),])))
  
  # two representations of the correct tree topology
  print(sum(abs(get(paste("ape_paml_Tree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = "")) - get(paste("PAML_estimatedTau_", toString(IGC.geo), ".0_1stTree_summary", sep = ""))[rownames(get(paste("ape_paml_Tree_1_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""))), ])))
  print(sum(abs(get(paste("ape_paml_Tree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = "")) - get(paste("PAML_estimatedTau_", toString(IGC.geo), ".0_2ndTree_summary", sep = ""))[rownames(get(paste("ape_paml_Tree_2_geo_", toString(IGC.geo), ".0_blen_summary", sep = ""))), ])))
}
```

Now, repeat what I did.
```{r}
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",] < 0)
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",] < 0)
sum(PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",] < 0)

hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_1_summary["ll",] < 0],
     main = "lnL difference - local tree 1",
     xlab = "lnL difference")
hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_2_summary["ll",] < 0],
     main = "lnL difference - local tree 2",
     xlab = "lnL difference")
hist((PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",])[PAML_estimatedTau_3.0_1stTree_summary["ll",] - PAML_estimatedTau_3.0_LocalTree_3_summary["ll",] < 0],
     main = "lnL difference - local tree 3",
     xlab = "lnL difference")

# Define function for converting
convert.summary <- function(localTree, summary, vector.names){
  new.summary <- vector("numeric", length(vector.names))
  names(new.summary) <- vector.names
  if (localTree == 1){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- summary["N0_N5"]
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- 0.0
    new.summary["N1_N2"] <- summary["N0_N1"]
    new.summary["N1_castelliiYDR418W"] <- summary["N0_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N1_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N1_N2"]
    new.summary["N3_N4"] <- summary["N2_N3"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N2_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N3_N4"]
    new.summary["N4_mikataeYDR418W"] <- summary["N3_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N4_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N4_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N5_N6"]
    new.summary["N6_castelliiYEL054C"] <- summary["N5_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N6_N7"]
    new.summary["N7_bayanusYEL054C"] <- summary["N6_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N7_N8"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N7_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N8_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N8_N9"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N9_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N9_cerevisiaeYEL054C"]
  
    }
  else if (localTree == 2){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- 0.0
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- summary["N0_N1"]
    new.summary["N1_N2"] <- summary["N1_N2"]
    new.summary["N1_castelliiYDR418W"] <- summary["N1_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N2_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N2_N3"]
    new.summary["N3_N4"] <- summary["N3_N4"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N3_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N4_N5"]
    new.summary["N4_mikataeYDR418W"] <- summary["N4_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N5_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N5_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N0_N6"]
    new.summary["N6_castelliiYEL054C"] <- summary["N0_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N6_N7"]
    new.summary["N7_bayanusYEL054C"] <- summary["N6_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N7_N8"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N7_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N8_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N8_N9"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N9_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N9_cerevisiaeYEL054C"]
    }
  else if (localTree == 3){
    new.summary[1:3] <- summary[1:3]
    new.summary["N0_N6"] <- 0.0
    new.summary["N0_kluyveriYDR418W"] <- summary["N0_kluyveriYDR418W"]
    new.summary["N0_N1"] <- 0.0
    new.summary["N1_N2"] <- summary["N0_N1"]
    new.summary["N1_castelliiYDR418W"] <- summary["N0_castelliiYDR418W"]
    new.summary["N2_bayanusYDR418W"] <- summary["N1_bayanusYDR418W"]
    new.summary["N2_N3"] <- summary["N1_N2"]
    new.summary["N3_N4"] <- summary["N2_N3"]
    new.summary["N3_kudriavzeviiYDR418W"] <- summary["N2_kudriavzeviiYDR418W"]
    new.summary["N4_N5"] <- summary["N3_N4"]
    new.summary["N4_mikataeYDR418W"] <- summary["N3_mikataeYDR418W"]
    new.summary["N5_paradoxusYDR418W"] <- summary["N4_paradoxusYDR418W"]
    new.summary["N5_cerevisiaeYDR418W"] <- summary["N4_cerevisiaeYDR418W"]
    new.summary["N6_N7"] <- summary["N0_N5"]
    new.summary["N6_castelliiYEL054C"] <- summary["N0_castelliiYEL054C"]
    new.summary["N7_N8"] <- summary["N5_N6"]
    new.summary["N7_bayanusYEL054C"] <- summary["N5_bayanusYEL054C"]
    new.summary["N8_N9"] <- summary["N6_N7"]
    new.summary["N8_kudriavzeviiYEL054C"] <- summary["N6_kudriavzeviiYEL054C"]
    new.summary["N9_mikataeYEL054C"] <- summary["N7_mikataeYEL054C"]
    new.summary["N9_N10"] <- summary["N7_N8"]
    new.summary["N10_paradoxusYEL054C"] <- summary["N8_paradoxusYEL054C"]
    new.summary["N10_cerevisiaeYEL054C"] <- summary["N8_cerevisiaeYEL054C"]
    }
  else if (localTree == 4){
    new.summary[vector.names] <- summary[vector.names]
    }
  return (new.summary)
  }

for (IGC.geo in IGC.geo.list){
  max.lnL.summary <- NULL
  vector.names = rownames(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = "")))
  for (sim.num in 1:100){
    max.pos <- which.max(c(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_1_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_",paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_2_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_",paste(toString(IGC.geo), ".0", sep = ""), "_LocalTree_3_summary", sep = ""))["ll", sim.num],
                           get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = ""))["ll", sim.num]))
    if (max.pos < 4){
      new.summary <- convert.summary(max.pos, get(paste("PAML_estimatedTau", paste(toString(IGC.geo), ".0", sep = ""), "LocalTree", toString(max.pos), "summary", sep = "_"))[, sim.num], vector.names)
      }
    else{
      new.summary <- get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = ""))[, sim.num]
      }
    max.lnL.summary <- cbind(max.lnL.summary, new.summary)
    }
  row.names(max.lnL.summary) <- row.names(get(paste("PAML_estimatedTau_", paste(toString(IGC.geo), ".0", sep = ""), "_1stTree_summary", sep = "")))
  assign(paste("geo", paste(toString(IGC.geo), ".0", sep = ""), "PAML", "maxlnL", "summary", sep = "_"), max.lnL.summary)
  }
```

#### Feb 12 update

```{r}
# Now check asymmetry again using best lnL estimates from 4 tree topologies
maxlnL.PAML.omega.mean <- c(mean(geo_3.0_PAML_maxlnL_summary["omega", ]), mean(geo_10.0_PAML_maxlnL_summary["omega", ]),
                            mean(geo_50.0_PAML_maxlnL_summary["omega", ]), mean(geo_100.0_PAML_maxlnL_summary["omega", ]), 
                            mean(geo_500.0_PAML_maxlnL_summary["omega", ]))
maxlnL.PAML.omega.sd <- c(sd(geo_3.0_PAML_maxlnL_summary["omega", ]), sd(geo_10.0_PAML_maxlnL_summary["omega", ]),
                          sd(geo_50.0_PAML_maxlnL_summary["omega", ]), sd(geo_100.0_PAML_maxlnL_summary["omega", ]), 
                          sd(geo_500.0_PAML_maxlnL_summary["omega", ]))

plot(IGC.geo.list, maxlnL.PAML.omega.mean)
abline(h = 1.0)

plot(IGC.geo.list, maxlnL.PAML.omega.sd)

maxlnL.PAML.kappa.mean <- c(mean(geo_3.0_PAML_maxlnL_summary["kappa", ]), mean(geo_10.0_PAML_maxlnL_summary["kappa", ]),
                            mean(geo_50.0_PAML_maxlnL_summary["kappa", ]), mean(geo_100.0_PAML_maxlnL_summary["kappa", ]), 
                            mean(geo_500.0_PAML_maxlnL_summary["kappa", ]))
maxlnL.PAML.kappa.sd <- c(sd(geo_3.0_PAML_maxlnL_summary["kappa", ]), sd(geo_10.0_PAML_maxlnL_summary["kappa", ]),
                          sd(geo_50.0_PAML_maxlnL_summary["kappa", ]), sd(geo_100.0_PAML_maxlnL_summary["kappa", ]), 
                          sd(geo_500.0_PAML_maxlnL_summary["kappa", ]))

plot(IGC.geo.list, maxlnL.PAML.kappa.mean)
abline(h = 8.4043336)

plot(IGC.geo.list, maxlnL.PAML.kappa.sd)
```

Now start to look at branch length estimates

Branch lengths used in simulation:

| Branch | blen |
|--------|------|
|N0_N1:         | 0.0197240946542 |
|N0_kluyveri    | 0.215682181791  |
|N1_N2          | 0.20925129872   |
|N1_castellii   | 0.171684721483  |
|N2_N3          | 0.0257112589202 |
|N2_bayanus     | 0.0266075664688 |
|N3_N4          | 0.0321083243449 |
|N3_kudriavzevii| 0.0853588718458 |
|N4_N5          | 0.024947887926  |
|N4_mikatae     | 0.0566627496729 |
|N5_cerevisiae  | 0.0581451177847 |
|N5_paradoxus   | 0.0218788166581 |

```{r}
# N0_N1
IGC.N0.N1.mean.list <- c(mean(geo_3.0_summary["(N0,N1)", ]), mean(geo_10.0_summary["(N0,N1)", ]),
                         mean(geo_50.0_summary["(N0,N1)", ]), mean(geo_100.0_summary["(N0,N1)", ]),
                         mean(geo_500.0_summary["(N0,N1)", ]))
IGC.N0.N1.sd.list <- c(sd(geo_3.0_summary["(N0,N1)", ]), sd(geo_10.0_summary["(N0,N1)", ]),
                       sd(geo_50.0_summary["(N0,N1)", ]), sd(geo_100.0_summary["(N0,N1)", ]),
                       sd(geo_500.0_summary["(N0,N1)", ]))

PAML.N0.N1.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_N1", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N0_N1", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N0_N1", ]))
PAML.N0.N1.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_N1", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N0_N1", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N0_N1", ]))
PAML.N0.N1.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_N6", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N0_N6", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N0_N6", ]))
PAML.N0.N1.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_N6", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N0_N6", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N0_N6", ]))
# N0_kluyveri
IGC.N0.kluyveri.mean.list <- c(mean(geo_3.0_summary["(N0,kluyveri)", ]), mean(geo_10.0_summary["(N0,kluyveri)", ]),
                               mean(geo_50.0_summary["(N0,kluyveri)", ]), mean(geo_100.0_summary["(N0,kluyveri)", ]),
                               mean(geo_500.0_summary["(N0,kluyveri)", ]))
IGC.N0.kluyveri.sd.list <- c(sd(geo_3.0_summary["(N0,kluyveri)", ]), sd(geo_10.0_summary["(N0,kluyveri)", ]),
                             sd(geo_50.0_summary["(N0,kluyveri)", ]), sd(geo_100.0_summary["(N0,kluyveri)", ]),
                             sd(geo_500.0_summary["(N0,kluyveri)", ]))
PAML.N0.kluyveri.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]), 
                                         mean(geo_10.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_50.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_100.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         mean(geo_500.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]))
PAML.N0.kluyveri.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N0_kluyveriYDR418W", ] ))
# N1_N2
IGC.N1.N2.mean.list <- c(mean(geo_3.0_summary["(N1,N2)", ]), mean(geo_10.0_summary["(N1,N2)", ]),
                         mean(geo_50.0_summary["(N1,N2)", ]), mean(geo_100.0_summary["(N1,N2)", ]),
                         mean(geo_500.0_summary["(N1,N2)", ]))
IGC.N1.N2.sd.list <- c(sd(geo_3.0_summary["(N1,N2)", ]), sd(geo_10.0_summary["(N1,N2)", ]),
                       sd(geo_50.0_summary["(N1,N2)", ]), sd(geo_100.0_summary["(N1,N2)", ]),
                       sd(geo_500.0_summary["(N1,N2)", ]))

PAML.N1.N2.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N1_N2", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N1_N2", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N1_N2", ]))
PAML.N1.N2.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N1_N2", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N1_N2", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N1_N2", ]))
PAML.N1.N2.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N6_N7", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N6_N7", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N6_N7", ]))
PAML.N1.N2.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N6_N7", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N6_N7", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N6_N7", ]))

# N1_castellii
IGC.N1.castellii.mean.list <- c(mean(geo_3.0_summary["(N1,castellii)", ]), mean(geo_10.0_summary["(N1,castellii)", ]),
                                mean(geo_50.0_summary["(N1,castellii)", ]), mean(geo_100.0_summary["(N1,castellii)", ]),
                                mean(geo_500.0_summary["(N1,castellii)", ]))
IGC.N1.castellii.sd.list <- c(sd(geo_3.0_summary["(N1,castellii)", ]), sd(geo_10.0_summary["(N1,castellii)", ]),
                              sd(geo_50.0_summary["(N1,castellii)", ]), sd(geo_100.0_summary["(N1,castellii)", ]),
                              sd(geo_500.0_summary["(N1,castellii)", ]))

PAML.N1.castellii.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]))
PAML.N1.castellii.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ]))

PAML.N1.castellii.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]))
PAML.N1.castellii.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ]))
# N2_N3
IGC.N2.N3.mean.list <- c(mean(geo_3.0_summary["(N2,N3)", ]), mean(geo_10.0_summary["(N2,N3)", ]),
                         mean(geo_50.0_summary["(N2,N3)", ]), mean(geo_100.0_summary["(N2,N3)", ]),
                         mean(geo_500.0_summary["(N2,N3)", ]))
IGC.N2.N3.sd.list <- c(sd(geo_3.0_summary["(N2,N3)", ]), sd(geo_10.0_summary["(N2,N3)", ]),
                       sd(geo_50.0_summary["(N2,N3)", ]), sd(geo_100.0_summary["(N2,N3)", ]),
                       sd(geo_500.0_summary["(N2,N3)", ]))

PAML.N2.N3.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N2_N3", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N2_N3", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N2_N3", ]))
PAML.N2.N3.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N2_N3", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N2_N3", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N2_N3", ]))
PAML.N2.N3.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N7_N8", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N7_N8", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N7_N8", ]))
PAML.N2.N3.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N7_N8", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N7_N8", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N7_N8", ]))
# N2_bayanus
IGC.N2.bayanus.mean.list <- c(mean(geo_3.0_summary["(N2,bayanus)", ]), mean(geo_10.0_summary["(N2,bayanus)", ]),
                              mean(geo_50.0_summary["(N2,bayanus)", ]), mean(geo_100.0_summary["(N2,bayanus)", ]),
                              mean(geo_500.0_summary["(N2,bayanus)", ]))
IGC.N2.bayanus.sd.list <- c(sd(geo_3.0_summary["(N2,bayanus)", ]), sd(geo_10.0_summary["(N2,bayanus)", ]),
                            sd(geo_50.0_summary["(N2,bayanus)", ]), sd(geo_100.0_summary["(N2,bayanus)", ]),
                            sd(geo_500.0_summary["(N2,bayanus)", ]))

PAML.N2.bayanus.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]))
PAML.N2.bayanus.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ]))
PAML.N2.bayanus.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]))
PAML.N2.bayanus.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ]))

# N3_N4
IGC.N3.N4.mean.list <- c(mean(geo_3.0_summary["(N3,N4)", ]), mean(geo_10.0_summary["(N3,N4)", ]),
                         mean(geo_50.0_summary["(N3,N4)", ]), mean(geo_100.0_summary["(N3,N4)", ]),
                         mean(geo_500.0_summary["(N3,N4)", ]))
IGC.N3.N4.sd.list <- c(sd(geo_3.0_summary["(N3,N4)", ]), sd(geo_10.0_summary["(N3,N4)", ]),
                       sd(geo_50.0_summary["(N3,N4)", ]), sd(geo_100.0_summary["(N3,N4)", ]),
                       sd(geo_500.0_summary["(N3,N4)", ]))
PAML.N3.N4.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N3_N4", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N3_N4", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N3_N4", ]))
PAML.N3.N4.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N3_N4", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N3_N4", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N3_N4", ]))
PAML.N3.N4.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N8_N9", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N8_N9", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N8_N9", ]))
PAML.N3.N4.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N8_N9", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N8_N9", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N8_N9", ]))
# N3_kudriavzevii
IGC.N3.kudriavzevii.mean.list <- c(mean(geo_3.0_summary["(N3,kudriavzevii)", ]), mean(geo_10.0_summary["(N3,kudriavzevii)", ]),
                                   mean(geo_50.0_summary["(N3,kudriavzevii)", ]), mean(geo_100.0_summary["(N3,kudriavzevii)", ]),
                                   mean(geo_500.0_summary["(N3,kudriavzevii)", ]))
IGC.N3.kudriavzevii.sd.list <- c(sd(geo_3.0_summary["(N3,kudriavzevii)", ]), sd(geo_10.0_summary["(N3,kudriavzevii)", ]),
                                 sd(geo_50.0_summary["(N3,kudriavzevii)", ]), sd(geo_100.0_summary["(N3,kudriavzevii)", ]),
                                 sd(geo_500.0_summary["(N3,kudriavzevii)", ]))
PAML.N3.kudriavzevii.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]), 
                                             mean(geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                             mean(geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]))
PAML.N3.kudriavzevii.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]), 
                                           sd(geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]),
                                           sd(geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ]))
PAML.N3.kudriavzevii.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]), 
                                             mean(geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                             mean(geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]))
PAML.N3.kudriavzevii.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]), 
                                           sd(geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]),
                                           sd(geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ]))
# N4_N5
IGC.N4.N5.mean.list <- c(mean(geo_3.0_summary["(N4,N5)", ]), mean(geo_10.0_summary["(N4,N5)", ]),
                         mean(geo_50.0_summary["(N4,N5)", ]), mean(geo_100.0_summary["(N4,N5)", ]),
                         mean(geo_500.0_summary["(N4,N5)", ]))
IGC.N4.N5.sd.list <- c(sd(geo_3.0_summary["(N4,N5)", ]), sd(geo_10.0_summary["(N4,N5)", ]),
                       sd(geo_50.0_summary["(N4,N5)", ]), sd(geo_100.0_summary["(N4,N5)", ]),
                       sd(geo_500.0_summary["(N4,N5)", ]))
PAML.N4.N5.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N4_N5", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N4_N5", ]))
PAML.N4.N5.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N4_N5", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N4_N5", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N4_N5", ]))
PAML.N4.N5.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N9_N10", ]), 
                                   mean(geo_10.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_50.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_100.0_PAML_maxlnL_summary["N9_N10", ]),
                                   mean(geo_500.0_PAML_maxlnL_summary["N9_N10", ]))
PAML.N4.N5.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N9_N10", ]), 
                                 sd(geo_10.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_50.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_100.0_PAML_maxlnL_summary["N9_N10", ]),
                                 sd(geo_500.0_PAML_maxlnL_summary["N9_N10", ]))
# N4_mikatae
IGC.N4.mikatae.mean.list <- c(mean(geo_3.0_summary["(N4,mikatae)", ]), mean(geo_10.0_summary["(N4,mikatae)", ]),
                              mean(geo_50.0_summary["(N4,mikatae)", ]), mean(geo_100.0_summary["(N4,mikatae)", ]),
                              mean(geo_500.0_summary["(N4,mikatae)", ]))
IGC.N4.mikatae.sd.list <- c(sd(geo_3.0_summary["(N4,mikatae)", ]), sd(geo_10.0_summary["(N4,mikatae)", ]),
                            sd(geo_50.0_summary["(N4,mikatae)", ]), sd(geo_100.0_summary["(N4,mikatae)", ]),
                            sd(geo_500.0_summary["(N4,mikatae)", ]))
PAML.N4.mikatae.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]))
PAML.N4.mikatae.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ]))
PAML.N4.mikatae.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]), 
                                        mean(geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                        mean(geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]))
PAML.N4.mikatae.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]), 
                                      sd(geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]),
                                      sd(geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ]))
# N5_cerevisiae
IGC.N5.cerevisiae.mean.list <- c(mean(geo_3.0_summary["(N5,cerevisiae)", ]), mean(geo_10.0_summary["(N5,cerevisiae)", ]),
                                 mean(geo_50.0_summary["(N5,cerevisiae)", ]), mean(geo_100.0_summary["(N5,cerevisiae)", ]),
                                 mean(geo_500.0_summary["(N5,cerevisiae)", ]))
IGC.N5.cerevisiae.sd.list <- c(sd(geo_3.0_summary["(N5,cerevisiae)", ]), sd(geo_10.0_summary["(N5,cerevisiae)", ]),
                               sd(geo_50.0_summary["(N5,cerevisiae)", ]), sd(geo_100.0_summary["(N5,cerevisiae)", ]),
                               sd(geo_500.0_summary["(N5,cerevisiae)", ]))
PAML.N5.cerevisiae.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]), 
                                           mean(geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                           mean(geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]))
PAML.N5.cerevisiae.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ]))
PAML.N5.cerevisiae.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]), 
                                           mean(geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                           mean(geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]))
PAML.N5.cerevisiae.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]), 
                                         sd(geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]),
                                         sd(geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ]))
# N5_paradoxus
IGC.N5.paradoxus.mean.list <- c(mean(geo_3.0_summary["(N5,paradoxus)", ]), mean(geo_10.0_summary["(N5,paradoxus)", ]),
                                mean(geo_50.0_summary["(N5,paradoxus)", ]), mean(geo_100.0_summary["(N5,paradoxus)", ]),
                                mean(geo_500.0_summary["(N5,paradoxus)", ]))
IGC.N5.paradoxus.sd.list <- c(sd(geo_3.0_summary["(N5,paradoxus)", ]), sd(geo_10.0_summary["(N5,paradoxus)", ]),
                              sd(geo_50.0_summary["(N5,paradoxus)", ]), sd(geo_100.0_summary["(N5,paradoxus)", ]),
                              sd(geo_500.0_summary["(N5,paradoxus)", ]))
PAML.N5.paradoxus.maxlnL.paralog1.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]))
PAML.N5.paradoxus.maxlnL.paralog1.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ]))
PAML.N5.paradoxus.maxlnL.paralog2.mean.list <- c(mean(geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]), 
                                          mean(geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                          mean(geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]))
PAML.N5.paradoxus.maxlnL.paralog2.sd.list <- c(sd(geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]), 
                                        sd(geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]),
                                        sd(geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ]))
```

Now plot same branch length estimates from each paralog in paml results and posterior branch length from IGC + MG94 model

```{r}
# N0_N1
matplot(IGC.geo.list, cbind(PAML.N0.N1.maxlnL.paralog1.mean.list, PAML.N0.N1.maxlnL.paralog2.mean.list, mean.post.N0.N1.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N0.N1 estimate")
abline(h = 0.0197240946542)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N0.N1.maxlnL.paralog1.sd.list, PAML.N0.N1.maxlnL.paralog2.sd.list, sd.post.N0.N1.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N0.N1 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N0_kluyveri
matplot(IGC.geo.list, cbind(PAML.N0.kluyveri.maxlnL.paralog1.mean.list, mean.post.N0.kluyveri.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N0.kluyveri estimate")
abline(h = 0.215682181791)
legend("right", legend = c("paralog1", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N0.kluyveri.maxlnL.paralog1.sd.list, sd.post.N0.kluyveri.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N0.kluyveri estimate")
legend("right", legend = c("paralog1", "posterior IGC"), col = 1:3, pch = 1)

# N1_N2
matplot(IGC.geo.list, cbind(PAML.N1.N2.maxlnL.paralog1.mean.list, PAML.N1.N2.maxlnL.paralog2.mean.list, mean.post.N1.N2.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N1.N2 estimate")
abline(h = 0.20925129872)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N1.N2.maxlnL.paralog1.sd.list, PAML.N1.N2.maxlnL.paralog2.sd.list, sd.post.N1.N2.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N1.N2 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N1_castellii
matplot(IGC.geo.list, cbind(PAML.N1.castellii.maxlnL.paralog1.mean.list, PAML.N1.castellii.maxlnL.paralog2.mean.list, mean.post.N1.castellii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N1.castellii estimate")
abline(h = 0.171684721483)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N1.castellii.maxlnL.paralog1.sd.list, PAML.N1.castellii.maxlnL.paralog2.sd.list, sd.post.N1.castellii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N1.castellii estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N2_N3
matplot(IGC.geo.list, cbind(PAML.N2.N3.maxlnL.paralog1.mean.list, PAML.N2.N3.maxlnL.paralog2.mean.list, mean.post.N2.N3.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N2.N3 estimate")
abline(h = 0.0257112589202)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N2.N3.maxlnL.paralog1.sd.list, PAML.N2.N3.maxlnL.paralog2.sd.list, sd.post.N2.N3.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N2.N3 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N2_bayanus
matplot(IGC.geo.list, cbind(PAML.N2.bayanus.maxlnL.paralog1.mean.list, PAML.N2.bayanus.maxlnL.paralog2.mean.list, mean.post.N2.bayanus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N2.bayanus estimate")
abline(h = 0.0266075664688)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N2.bayanus.maxlnL.paralog1.sd.list, PAML.N2.bayanus.maxlnL.paralog2.sd.list, sd.post.N2.bayanus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N2.bayanus estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N3_N4
matplot(IGC.geo.list, cbind(PAML.N3.N4.maxlnL.paralog1.mean.list, PAML.N3.N4.maxlnL.paralog2.mean.list, mean.post.N3.N4.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N3.N4 estimate")
abline(h = 0.0321083243449)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N3.N4.maxlnL.paralog1.sd.list, PAML.N3.N4.maxlnL.paralog2.sd.list, sd.post.N3.N4.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N3.N4 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N3_kudriavzevii
matplot(IGC.geo.list, cbind(PAML.N3.kudriavzevii.maxlnL.paralog1.mean.list, PAML.N3.kudriavzevii.maxlnL.paralog2.mean.list, mean.post.N3.kudriavzevii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N3.kudriavzevii estimate")
abline(h = 0.0853588718458)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N3.kudriavzevii.maxlnL.paralog1.sd.list, PAML.N3.kudriavzevii.maxlnL.paralog2.sd.list, sd.post.N3.kudriavzevii.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N3.kudriavzevii estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N4_N5
matplot(IGC.geo.list, cbind(PAML.N4.N5.maxlnL.paralog1.mean.list, PAML.N4.N5.maxlnL.paralog2.mean.list, mean.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.N5 estimate")
abline(h = 0.024947887926)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.N5.maxlnL.paralog1.sd.list, PAML.N4.N5.maxlnL.paralog2.sd.list, sd.post.N4.N5.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.N5 estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N4_mikatae
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.maxlnL.paralog1.mean.list, PAML.N4.mikatae.maxlnL.paralog2.mean.list, mean.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N4.mikatae estimate")
abline(h = 0.0566627496729)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N4.mikatae.maxlnL.paralog1.sd.list, PAML.N4.mikatae.maxlnL.paralog2.sd.list, sd.post.N4.mikatae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N4.mikatae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N5_cerevisiae
matplot(IGC.geo.list, cbind(PAML.N5.cerevisiae.maxlnL.paralog1.mean.list, PAML.N5.cerevisiae.maxlnL.paralog2.mean.list, mean.post.N5.cerevisiae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N5.cerevisiae estimate")
abline(h = 0.0581451177847)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N5.cerevisiae.maxlnL.paralog1.sd.list, PAML.N5.cerevisiae.maxlnL.paralog2.sd.list, sd.post.N5.cerevisiae.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N5.cerevisiae estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

# N5_paradoxus
matplot(IGC.geo.list, cbind(PAML.N5.paradoxus.maxlnL.paralog1.mean.list, PAML.N5.paradoxus.maxlnL.paralog2.mean.list, mean.post.N5.paradoxus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "mean N5.paradoxus estimate")
abline(h = 0.0218788166581)
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)
matplot(IGC.geo.list, cbind(PAML.N5.paradoxus.maxlnL.paralog1.sd.list, PAML.N5.paradoxus.maxlnL.paralog2.sd.list, sd.post.N5.paradoxus.list),
        type = c("p"), pch = 1, col = 1:3, ylab = "sd N5.paradoxus estimate")
legend("right", legend = c("paralog1", "paralog2", "posterior IGC"), col = 1:3, pch = 1)

```

Now start to check branches ratio of subtree branches of paralog 1 over paralog 2 ratios

Exclude all datasets that have the edge being examined estimated to 0.

```{r}
# IGC.geo = 3.0

# N0_N1
data.sets <- geo_3.0_PAML_maxlnL_summary["N0_N1", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N0_N6", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N0_N1", data.sets] / geo_3.0_PAML_maxlnL_summary["N0_N6", data.sets]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
data.sets <- geo_3.0_PAML_maxlnL_summary["N1_N2", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N6_N7", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N1_N2", data.sets] / geo_3.0_PAML_maxlnL_summary["N6_N7", data.sets]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
data.sets <- geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N1_castelliiYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N6_castelliiYEL054C", data.sets]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
data.sets <- geo_3.0_PAML_maxlnL_summary["N2_N3", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N7_N8", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N2_N3", data.sets] / geo_3.0_PAML_maxlnL_summary["N7_N8", data.sets]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
data.sets <- geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N2_bayanusYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N7_bayanusYEL054C", data.sets]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
data.sets <- geo_3.0_PAML_maxlnL_summary["N3_N4", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N8_N9", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N3_N4", data.sets] / geo_3.0_PAML_maxlnL_summary["N8_N9", data.sets]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
data.sets <- geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", data.sets]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
data.sets <- geo_3.0_PAML_maxlnL_summary["N4_N5", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N9_N10", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N4_N5", data.sets] / geo_3.0_PAML_maxlnL_summary["N9_N10", data.sets]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
data.sets <- geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N4_mikataeYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N9_mikataeYEL054C", data.sets] 
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
data.sets <- geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
data.sets <- geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ] > 5e-6 &  geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ] > 5e-6
target <- geo_3.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", data.sets] / geo_3.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)



```

```{r}
# IGC.geo = 10.0

# N0_N1
data.sets <- geo_10.0_PAML_maxlnL_summary["N0_N1", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N0_N6", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N0_N1", data.sets] / geo_10.0_PAML_maxlnL_summary["N0_N6", data.sets]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
data.sets <- geo_10.0_PAML_maxlnL_summary["N1_N2", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N6_N7", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N1_N2", data.sets] / geo_10.0_PAML_maxlnL_summary["N6_N7", data.sets]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
data.sets <- geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N1_castelliiYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N6_castelliiYEL054C", data.sets]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
data.sets <- geo_10.0_PAML_maxlnL_summary["N2_N3", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N7_N8", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N2_N3", data.sets] / geo_10.0_PAML_maxlnL_summary["N7_N8", data.sets]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
data.sets <- geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N2_bayanusYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N7_bayanusYEL054C", data.sets]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
data.sets <- geo_10.0_PAML_maxlnL_summary["N3_N4", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N8_N9", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N3_N4", data.sets] / geo_10.0_PAML_maxlnL_summary["N8_N9", data.sets]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
data.sets <- geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", data.sets]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
data.sets <- geo_10.0_PAML_maxlnL_summary["N4_N5", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N9_N10", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N4_N5", data.sets] / geo_10.0_PAML_maxlnL_summary["N9_N10", data.sets]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
data.sets <- geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N4_mikataeYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N9_mikataeYEL054C", data.sets] 
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
data.sets <- geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
data.sets <- geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ] > 5e-6 &  geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ] > 5e-6
target <- geo_10.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", data.sets] / geo_10.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)



```
```{r}
# IGC.geo = 50.0

# N0_N1
data.sets <- geo_50.0_PAML_maxlnL_summary["N0_N1", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N0_N6", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N0_N1", data.sets] / geo_50.0_PAML_maxlnL_summary["N0_N6", data.sets]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
data.sets <- geo_50.0_PAML_maxlnL_summary["N1_N2", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N6_N7", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N1_N2", data.sets] / geo_50.0_PAML_maxlnL_summary["N6_N7", data.sets]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
data.sets <- geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N1_castelliiYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N6_castelliiYEL054C", data.sets]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
data.sets <- geo_50.0_PAML_maxlnL_summary["N2_N3", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N7_N8", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N2_N3", data.sets] / geo_50.0_PAML_maxlnL_summary["N7_N8", data.sets]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
data.sets <- geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N2_bayanusYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N7_bayanusYEL054C", data.sets]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
data.sets <- geo_50.0_PAML_maxlnL_summary["N3_N4", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N8_N9", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N3_N4", data.sets] / geo_50.0_PAML_maxlnL_summary["N8_N9", data.sets]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
data.sets <- geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", data.sets]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
data.sets <- geo_50.0_PAML_maxlnL_summary["N4_N5", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N9_N10", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N4_N5", data.sets] / geo_50.0_PAML_maxlnL_summary["N9_N10", data.sets]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
data.sets <- geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N4_mikataeYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N9_mikataeYEL054C", data.sets] 
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
data.sets <- geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
data.sets <- geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ] > 5e-6 &  geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ] > 5e-6
target <- geo_50.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", data.sets] / geo_50.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)



```

```{r}
# IGC.geo = 100.0

# N0_N1
data.sets <- geo_100.0_PAML_maxlnL_summary["N0_N1", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N0_N6", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N0_N1", data.sets] / geo_100.0_PAML_maxlnL_summary["N0_N6", data.sets]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
data.sets <- geo_100.0_PAML_maxlnL_summary["N1_N2", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N6_N7", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N1_N2", data.sets] / geo_100.0_PAML_maxlnL_summary["N6_N7", data.sets]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
data.sets <- geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N1_castelliiYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N6_castelliiYEL054C", data.sets]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
data.sets <- geo_100.0_PAML_maxlnL_summary["N2_N3", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N7_N8", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N2_N3", data.sets] / geo_100.0_PAML_maxlnL_summary["N7_N8", data.sets]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
data.sets <- geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N2_bayanusYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N7_bayanusYEL054C", data.sets]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
data.sets <- geo_100.0_PAML_maxlnL_summary["N3_N4", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N8_N9", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N3_N4", data.sets] / geo_100.0_PAML_maxlnL_summary["N8_N9", data.sets]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
data.sets <- geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", data.sets]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
data.sets <- geo_100.0_PAML_maxlnL_summary["N4_N5", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N9_N10", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N4_N5", data.sets] / geo_100.0_PAML_maxlnL_summary["N9_N10", data.sets]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
data.sets <- geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N4_mikataeYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N9_mikataeYEL054C", data.sets] 
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
data.sets <- geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
data.sets <- geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ] > 5e-6 &  geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ] > 5e-6
target <- geo_100.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", data.sets] / geo_100.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)



```

```{r}
# IGC.geo = 500.0

# N0_N1
data.sets <- geo_500.0_PAML_maxlnL_summary["N0_N1", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N0_N6", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N0_N1", data.sets] / geo_500.0_PAML_maxlnL_summary["N0_N6", data.sets]
hist(target, main = "N0_N1"); mean(target); sd(target)

# N1_N2
data.sets <- geo_500.0_PAML_maxlnL_summary["N1_N2", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N6_N7", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N1_N2", data.sets] / geo_500.0_PAML_maxlnL_summary["N6_N7", data.sets]
hist(target, main = "N1_N2"); mean(target); sd(target)

# N1_castellii
data.sets <- geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N1_castelliiYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N6_castelliiYEL054C", data.sets]
hist(target, main = "N1_castellii"); mean(target); sd(target)

# N2_N3
data.sets <- geo_500.0_PAML_maxlnL_summary["N2_N3", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N7_N8", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N2_N3", data.sets] / geo_500.0_PAML_maxlnL_summary["N7_N8", data.sets]
hist(target, main = "N2_N3"); mean(target); sd(target)

# N2_bayanus
data.sets <- geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N2_bayanusYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N7_bayanusYEL054C", data.sets]
hist(target, main = "N2_bayanus"); mean(target); sd(target)

# N3_N4
data.sets <- geo_500.0_PAML_maxlnL_summary["N3_N4", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N8_N9", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N3_N4", data.sets] / geo_500.0_PAML_maxlnL_summary["N8_N9", data.sets]
hist(target, main = "N3_N4"); mean(target); sd(target)

# N3_kudriavzevii
data.sets <- geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N3_kudriavzeviiYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N8_kudriavzeviiYEL054C", data.sets]
hist(target, main = "N3_kudriavzevii"); mean(target); sd(target)

# N4_N5
data.sets <- geo_500.0_PAML_maxlnL_summary["N4_N5", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N9_N10", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N4_N5", data.sets] / geo_500.0_PAML_maxlnL_summary["N9_N10", data.sets]
hist(target, main = "N4_N5"); mean(target); sd(target)

# N4_mikatae
data.sets <- geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N4_mikataeYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N9_mikataeYEL054C", data.sets] 
hist(target, main = "N4_mikatae"); mean(target); sd(target)

# N5_paradoxus
data.sets <- geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N5_paradoxusYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N10_paradoxusYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_paradoxus"); mean(target); sd(target)

# N5_cerevisiae
data.sets <- geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", ] > 5e-6 &  geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", ] > 5e-6
target <- geo_500.0_PAML_maxlnL_summary["N5_cerevisiaeYDR418W", data.sets] / geo_500.0_PAML_maxlnL_summary["N10_cerevisiaeYEL054C", data.sets]  # paralog 1 / paralog 2
hist(target, main = "N5_cerevisiae"); mean(target); sd(target)



```

